pathway coverage

### 2019-11-27 scripts/11_lefse_geneorthologs.Rmd
the regroup

```{r}
# loading the table with the valid sampleids
pheno <- read_csv('../data/current_pheno.csv') %>% 
  filter(! Sampleid %in% c("1725E", "2222A" ,"2245A"))

@@

## Reorder the GO stratified table

>>>>

```{r}
# loading the table with the valid sampleids
pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv')

@@

## Reorder the KO stratified table

```{bash}
# get the KO regrouped table
humann2_regroup_table \
            --input ../data/humann2_res/humann2_genefamilies.tsv  \
            --groups uniref90_ko  \
            --output ../data/humann2_res/humann2_genefamilies_KO_regroup.tsv
```

### 2019-11-27 scripts/24_pathcoverage.Rmd
the regroup

pwc_sig_tox %>% 
  ggplot(aes(x = pw, y = cov_med, fill = Toxicity)) +
  geom_bar( stat = 'identity' , position="dodge") +
  coord_flip() +
  scale_color_manual(values = c('#0099B4', '#AD002A'))  +
  scale_fill_manual(values = c('#0099B4', '#AD002A')) +
  theme_classic() +
  theme(axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=axis_text_fs),
        plot.title = element_text(size=all_title_fs),
        axis.text.x = element_text(size=axis_text_fs),
        legend.position="bottom") +
  labs(title = str_glue('Response to Toxicity') ,
       y = 'Median coverage in each group') + 
  ggsave('../figs/path_coverage_tox.jpg', width = 15, height = 8, dpi = 300)

@@

pwc_sig_cr %>% 
  ggplot(aes(x = pw, y = cov_med, fill = CR)) +
  geom_bar( stat = 'identity' , position="dodge") +
  coord_flip() +
  scale_color_manual(values = c('#ED0000', '#00468B'))  +
  scale_fill_manual(values = c('#ED0000', '#00468B')) +
  theme_classic() +
  theme(axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=axis_text_fs),
        plot.title = element_text(size=all_title_fs),
        axis.text.x = element_text(size=axis_text_fs),
        legend.position="bottom") +
  labs(title = str_glue('Response to CR') ,
       y = 'Median coverage in each group') + 
  ggsave('../figs/path_coverage_CR.jpg', width = 15, height = 8, dpi = 300)
```

```{r}
# try to do a heatmap to see if there is some sample that is interesting to look at 
pheatmap(
  pwc_wide,
  #color=bwrPalette, 
  #annotation_col = annot,
  show_rownames = T,
  show_colnames = TRUE,
  filename = '../figs/pcov_hm.jpg',
  height = 10,
  width = 20,
  cluster_rows =T,
  cluster_cols=T
)
```

>>>>

tox <- pwc_sig_tox %>% 
  ggplot(aes(x = pw, y = cov_med, fill = Toxicity)) +
  geom_bar( stat = 'identity' , position="dodge") +
  coord_flip() +
  scale_color_manual(values = c('#0099B4', '#AD002A'))  +
  scale_fill_manual(values = c('#0099B4', '#AD002A')) +
  theme_classic() +
  theme(axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=axis_text_fs),
        plot.title = element_text(size=all_title_fs),
        axis.text.x = element_text(size=axis_text_fs),
        legend.position="bottom") +
  labs(title = str_glue('Response to Toxicity') ,
       y = 'Median coverage in each group') + 
  ggsave('../figs/path_coverage_tox.jpg', width = 15, height = 8, dpi = 300)

@@

cr <- pwc_sig_cr %>% 
  ggplot(aes(x = pw, y = cov_med, fill = CR)) +
  geom_bar( stat = 'identity' , position="dodge") +
  coord_flip() +
  scale_color_manual(values = c('#ED0000', '#00468B'))  +
  scale_fill_manual(values = c('#ED0000', '#00468B')) +
  theme_classic() +
  theme(axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=axis_text_fs),
        plot.title = element_text(size=all_title_fs),
        axis.text.x = element_text(size=axis_text_fs),
        legend.position="bottom") +
  labs(title = str_glue('Response to CR') ,
       y = 'Median coverage in each group') + 
  ggsave('../figs/path_coverage_CR.jpg', width = 15, height = 8, dpi = 300)
```

```{r}
# try to do a heatmap to see if there is some sample that is interesting to look at 
annot <- pheno %>% 
  column_to_rownames('sampleid')

pheatmap(
  pwc_wide,
  #color=bwrPalette, 
  annotation_col = annot,
  show_rownames = T,
  show_colnames = TRUE,
  filename = '../figs/pcov_hm.jpg',
  height = 10,
  width = 20,
  cluster_rows =T,
  cluster_cols=T
)
```
